We would like to think we did ok for this project, although there are many things that could be improved upon. \\\\ Some examples of what we think could be improved upon are the implementation of fuzzy logic. We currently have strangely formed FLV's that do however seem to work. When changing the graphs to be a normal format we have a bug where the defuzzification of the distance to the enemy always seems to return 0 and therefore we decided to keep the graphs the way they were. \\\\ We also think the enemy/entity implementation we have could be improved on. We only later discovered the source found within the book and we already had the enemy-hierarchy implemented. after that we decided to implement the entity-hierarchy like the book did but the combination of both creates awkward situations such as the eagle not being an Enemy. \\\\ We think the main difficulties we had with the project were finding about the book source too late and partly because of that, not being ready for the deadline. After the deadline we both were quite busy with the game project and had to work on the Tower Defense game during the weekends mainly which isn't a great excuse but it lead to us taking so long to hand this in. \\\\ On the more positive side we think we implemented most required features or atleast tried to implement them, We feel like we have some good parts within the code unlike the enemy-entity system. Such as the Powerup hierarchy for the explore and being able to specify a Queue of Powerups for the Flying Entity to explore, it would be very easy to expand this to include different kinds of Powerups. We also think we did a decent job on commenting the code and staying consistent with our conventions.